### 2022-09-02 main/chapter_searches.tex
some proofreading

Coin tosses, for example, can be imagined as random.
Earth's human population could toss a few billion coins to precisely
establish a probability of landing heads from the ratio of
$n$ (number of heads) to $N$ (number of tosses).
But suppose you are given a red envelope containing a coin ---
which way up is the coin in the envelope?
You could guess or bet on the answer, and that decision might involve a tacitly
assumed probability.
A frequency, however, would only be permitted if the envelope had been packaged
randomly.
Was the coin first tossed to randomize its face, or placed deliberately?
It is unclear.

Tom Stoppard's play `Rosencrantz and Guildenstern Are Dead'~\cite{
stoppard1967rosencrantz
}
contains a clearer example ---
Rosencrantz and Guildenstern toss a coin ninety-two times, all landing heads
(by ``un-, sub- or supernatural forces'').
They play a game with a third player, landing eight more heads.
Is the next toss heads or tails?
The answer is not random --- it is burned in print onto paper, so no frequency
can be assigned.
Were subjective probabilities permitted, you could predict the result, and that
prediction would be subjectively informed by it being the one-hundred-and-first
toss, our cultural entanglement with round numbers in base-10, and your reading
of these words.
Frequentist theory, however, forbids such subjective probabilities of
non-random unknowns, so is left seeking alternatives.

As established in Section~\ref{sec:searches_data_analysis}, the original
probability theory of Laplace and Bayes, did not require frequency
interpretations; these were developed later in the 19th century by
mathematicians including Venn~\cite{venn1866logic} and
Boole~\cite{boole1854investigation}, in reactions that may well have been
propelled by reasonable objections to flawed posterior-only methods.
Modern frequentist theory has a rigorous set-theoretic formulation in the
Kolmogorov axioms~\cite{
kolomogoroff1933de,
kolomogoroff1950translated,
axioms1010038
}.
Applied frequentist methods, unlike frequentist theory, are constrained with
considerably less precision --- the denial of certain (non-frequency)
probabilities does not construct their replacements, and various surrogates
have evolved.
Modern frequentist methods are largely attributable to the authors
R. A. Fisher (for likelihood, $p$-values, and estimation criteria), and
J. Neyman and E. S. Pearson
(for statistical hypothesis testing and confidence intervals).
Together these do not form a harmonious or consistent framework ---
the two groups have emphatic disagreements in print ---
but do cover many practices that continue to survive in modern science
and explain important features of the methods apply to LHC data, which will be
introduced in Section~\ref{sec:searches_practice}.

>>>>

Coin tosses, for example, can be imagined as random.
Earth's human population could toss a few billion coins to precisely
establish a probability of landing heads from the ratio of
$n$ (number of heads) to $N$ (number of tosses).
Now suppose you are given a red envelope containing a coin;
which way up is the coin in the envelope?
You could guess or bet on the answer, and that decision might involve a tacitly
assumed probability.
A frequency, however, would only be permitted if the envelope had been packaged
randomly.
Was the coin first tossed to randomize its face, or placed deliberately?
It is unclear.

Tom Stoppard's play `Rosencrantz and Guildenstern Are Dead'~\cite{
stoppard1967rosencrantz
}
opens with a clearer example ---
the titular characters toss a coin ninety-two times, all landing heads
(by ``un-, sub- or supernatural forces'').
They then play a game with a third player, landing eight more heads.
Will the next toss be heads or tails?
The answer is not random --- it is burned in print onto paper, so no frequency
can be assigned.
Were subjective probabilities permitted, you could predict the result, and that
prediction would be subjectively informed by it being the one-hundred-and-first
toss, our cultural entanglement with round numbers in base-10, and your reading
of these words.
Frequentist theory, however, forbids such subjective probabilities of
non-random unknowns, so is left seeking alternatives.

As established in Section~\ref{sec:searches_data_analysis}, the original
probability theory of Laplace and Bayes did not require frequency
interpretations; these were developed later in the 19th century by
mathematicians including Venn~\cite{venn1866logic} and
Boole~\cite{boole1854investigation}, in reactions that may well have been
propelled by reactions to flawed posterior-only methods.
Modern frequentist theory has a rigorous set-theoretic formulation in the
Kolmogorov axioms~\cite{
kolomogoroff1933de,
kolomogoroff1950translated,
axioms1010038
}, but applied frequentist methods, are constrained with considerably less
precision --- the denial of certain (non-frequency) probabilities does not
construct their replacements, and various surrogates have evolved.

Modern frequentist methods are largely attributable to the authors
R. A. Fisher (for likelihood, $p$-values, and estimation criteria), and
J. Neyman and E. S. Pearson
(for statistical hypothesis testing and confidence intervals).
Together these do not form a harmonious framework;
the two groups have emphatic disagreements in print, but together they
do cover many practices that survive in modern science and explain important
features of the methods we apply to LHC data, which will be introduced in
Section~\ref{sec:searches_practice}.
